---
title: "YOUR TURN! `r params$import_species`"
author: "kat leigh"
output: html_document
params:
  import_species: Chinstrap
---

### Your job: create a parameterized report using data from `penguins.csv`. 
- Your report should contain a ggplot graph of flipper length versus body mass for the **species** that you choose.
penguins
- In the `render_functions.R` script, create a function that will render the report for the species you pick, saved as an .html with format 'penguin_report_SPECIESNAME.html'. 

- In the `render_functions.R` script, write a for loop that will automatically render a separate report for *all species* in the data. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
```

```{r}

ggplot(data = filter(penguins, species == params$import_species), aes(x = flipper_length_mm,
                 y = body_mass_g,
                 color = sex)) + 
  geom_point()+
  geom_smooth(alpha = .2)+
  theme_minimal()+
  labs(title = paste0(params$import_species, " penguin flipper lengths versus body masses by sex"),
       caption = "Data from palmerpenguins package",
       x = 'Flipper Length (mm)',
       y = 'Body Mass (g)')

```

